### 2023-11-14 manuscript/supplementary_tables.Rmd
Remove 13C2 isotope from Table S3, Additional file 3

```{r table-s3}
mzAnnotation::isotope_rules() %>% 
  dplyr::filter(Isotope %in% c('13C','13C2','18O','34S')) %>% 
  dplyr::select(Isotope,
                `Mass difference` = `Mass Difference`) %>%
  dplyr::mutate(Isotope = c('\\textsuperscript{13}C',
                            '\\textsuperscript{13}C2',
                            '\\textsuperscript{18}O',
                            '\\textsuperscript{34}S')) %>% 
  knitr::kable(caption = 'Isotopic mass difference information.',
               format = 'latex',
               escape = FALSE,
               booktabs = TRUE)
```

>>>>

```{r table-s3}
mzAnnotation::isotope_rules() %>% 
  dplyr::filter(Isotope %in% c('13C','18O','34S')) %>% 
  dplyr::select(Isotope,
                `Mass difference` = `Mass Difference`) %>%
  dplyr::mutate(Isotope = c('\\textsuperscript{13}C',
                            '\\textsuperscript{18}O',
                            '\\textsuperscript{34}S')) %>% 
  knitr::kable(caption = 'Isotopic mass difference information.',
               format = 'latex',
               escape = FALSE,
               booktabs = TRUE)
```
